Open Clusters Characterization in Gaia DR2 Using ML Algorithms

### 2020-10-23 thesis/thesis.tex
thesis: Add GitHub QR code
thesis: Update figures
thesis: First corrections

\usepackage{caption}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subcaption}

@@

@@

Stellar open clusters (OC) are groups of stars gravitationally bound originated from a single molecular gas cloud.
Thus they share the same chemical composition and age, and they have similar relative positions and proper motion.
These astronomical objects are of fundamental importance to understand the spiral structure,
the dynamics and the chemical evolution of our galaxy.

@@

\chapter{Context and State of the Art}

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_melotte_22.pdf}
    \caption{Proper motions}
    \label{fig:pm_melotte_22}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_melotte_22.pdf}
    \caption{Proper motions with vector lines}
    \label{fig:pm_vec_melotte_22}
  \end{subfigure}
  \caption{Open Cluster Melotte 22 (M45)}
\end{figure}

However, in general it is not as easy and becomes necessary to take into account other parameters such as distances, or even
metallicity and age (derived from isochrone curves) and requires photometric data from stars in the studied field.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_ngc_2353.pdf}
    \caption{Proper motions}
    \label{fig:pm_ngc_2353}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/parallax_ngc_2353.pdf}
    \caption{Parallax histogram}
    \label{fig:parallax_ngc_2353}
  \end{subfigure}
  \caption{Open Cluster NGC 2353}
\end{figure}

The first one is a non-parametrized method. It determines empirically the frequency functions asociated to astrometrical variables
without making any assumption about their profiles. However, it heavily does depend on the initial field selection and other
parameters related to frequency functions. \emph{Clusterix 2.0.} is presented as a web app tool inside the Spanish Virtual Observatory
(VO) framework and works together with other VO tool such as:
\emph{TOPCAT} \cite[][\url{http://www.starlink.ac.uk/topcat/}]{taylor2005topcat},
\emph{Aladin} \cite[][\url{https://aladin.u-strasbg.fr/aladin.gml}]{bonnarel2000aladin},
\emph{VOSA} \cite[][\url{http://svo2.cab.inta-csic.es/theory/vosa/}]{bayo2008vosa}, etc.

\chapter{Aims}

@@

\begin{itemize}
  \item OCs and stars \emph{right ascension}: $\alpha$ and \emph{declination}: $\delta$
  \item OCs \emph{estimated sizes}: $r$
  \item \emph{Proper motion}: $\mu_{\alpha}$, $\mu_{\delta}$ and \emph{parallax}: $\varpi$
  \item \emph{Photometric}: $E(B-R)$, $G_{mag}$
  \item \emph{Radial velocity}: $RV$
  \item \emph{Associated errors} will be taken into account to estimate prediction errors
\end{itemize}

@@

@@

\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

>>>>

\usepackage{caption}
\usepackage{eso-pic}
\usepackage{float}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{picture}
\usepackage{subcaption}

@@

\chapter{Acknowledgement}

@@

Stellar open clusters (OC) \cite[]{janes1982open} are groups of stars gravitationally bound originated from a single molecular gas cloud.
Thus they share the same chemical composition and age, and they have similar relative positions and proper motion.
These astronomical objects are of fundamental importance to understand the spiral structure,
the dynamics and the chemical evolution of our galaxy.

@@

\section{Aims}

@@

\begin{itemize}
  \item OCs and stars \emph{right ascension}: $\alpha$ and \emph{declination}: $\delta$
  \item OCs \emph{estimated sizes}: $r$
  \item \emph{Proper motion}: $\mu_{\alpha}$, $\mu_{\delta}$ and \emph{parallax}: $\varpi$
  \item \emph{Photometric}: $E(B-R)$, $G_{mag}$
  \item \emph{Associated errors} will be taken into account to estimate prediction errors
\end{itemize}

@@

\chapter{State of the Art}

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_melotte_22.pdf}
    \caption{Proper motions}
    \label{fig:pm_melotte_22}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/parallax_melotte_22.pdf}
    \caption{Parallax}
    \label{fig:pm_vec_melotte_22}
  \end{subfigure}
  \caption{Open Cluster Melotte 22 (M45)}
\end{figure}

However, in general it is not as easy and becomes necessary to consider other parameters such as distances, or even
metallicity and age (derived from isochrone curves) and requires photometric data from stars in the studied field.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/pm_ngc_2682.pdf}
    \caption{Proper motions}
    \label{fig:pm_ngc_2682}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/isochrone_ngc_2682.pdf}
    \caption{Isochrone curve}
    \label{fig:parallax_ngc_2682}
  \end{subfigure}
  \caption{Open Cluster NGC 2682}
\end{figure}

The first one is a non-parametrized method. It determines empirically the frequency functions asociated to astrometrical variables
without making any assumption about their profiles. However, it heavily does depend on the initial field selection and other
parameters related to frequency functions. \emph{Clusterix 2.0.} is a web app tool inside the Spanish Virtual Observatory
(VO) framework and works together with other VO tool such as:
\emph{TOPCAT} \cite[][\url{http://www.starlink.ac.uk/topcat/}]{taylor2005topcat},
\emph{Aladin} \cite[][\url{https://aladin.u-strasbg.fr/aladin.gml}]{bonnarel2000aladin},
\emph{VOSA} \cite[][\url{http://svo2.cab.inta-csic.es/theory/vosa/}]{bayo2008vosa}, etc.

@@
